Minimizing post-shock forecasting error through aggregation of outside information

### 2021-02-02 Revision/manuscript.tex
made minor updates to manuscript

\begin{figure*}[t!]
  \begin{center}
    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
  \end{center}
     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$. (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series. (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.  The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool. $\hat{y}^{1}_{T_1^*+1}$ is the prediction without scalar adjustment of $\hat{\alpha}$ whereas $\hat{y}^{2}_{T_1^*+1}$ is the one with. In this example,
    they differ only by an adjustment $\hat{\alpha}=10.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
\end{figure*}

>>>>

\begin{figure*}[t!]
  \begin{center}
    \subfloat[]{\includegraphics[height = 5.5cm]{FIG1a.pdf}}\\
     \subfloat[]{\includegraphics[height = 5.5cm]{FIG1b.pdf}}
  \end{center}
     \caption{The time series experience a shock at $T_1^*+1=126$ with true shock effect $\alpha = 9.21$. (a) presents the comparison of the prediction without adjustment and one that uses simple averaging of estimated shock effects given a donor pool of $n=40$ time series. (b) shows the histogram for the least square estimates $\hat{\alpha}_i$s used in estimating shock $\alpha_1$ for $i = 2, \ldots, 41$.  The magenta dots represent $\hat{\alpha}_i$ from the time series forming the donor pool. $\hat{y}^{1}_{T_1^*+1}$ is the prediction without any adjustment, and $\hat{y}^{2}_{T_1^*+1}$ is the forecast with additive adjustment of $\hat{\alpha} = n^{-1}\sum_{i=2}^{n+1}\hat\alpha_i$. In this example, theses forecasts differ by $\hat{\alpha}=10.22$. It is clear that $\hat{y}^{2}_{T_1^*+1}$ performs better than $\hat{y}^{1}_{T_1^*+1}$.}\label{figure1}
\end{figure*}
